### 2018-05-03 papers/synth/example.tex

>>>>

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
  \node[main node] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
  \node[main node] (ic) [below right of=ga,yshift=7mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
  \node[main node] (er) [below of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
  \node[main node] (ee) [left of=ga] {EE};
  \node[main node] (le) [below of=ee] {LE};
  \path (ic) edge[bend right] node [right] {\^{Qc6}} (ga);
  \path (er) edge[bend left] node [left] {R6} (ga);
  \path (er) edge[bend right] node [left] {\^{Qc6}} (ga);
  \path (er) edge[bend right] node [right] {\^{Qc6}} (ic);
  \path (ga) edge[bend right=80] node [right] {\^{Qc1}} (er);
  \path (ee) edge[bend left] node [left] {\^{R8},Qa7,Qbc7,R7} (le);
  \end{tikzpicture}
  \caption{found-in-nature VTS}
  \label{fig:mukund-vts}
\end{figure}

In figure~\ref{fig:mukund-vts}
